Political Support in the United States

### 2024-03-17 paper/paper.qmd
Update paper.qmd

## Measurements 
## Measurements 
The collected dataset from the Cooperative Election Study (CES) offers a comprehensive view of U.S. adult citizens' electoral behaviors, political opinions, and demographic characteristics. The CES 2022 dataset, gathered through an online survey by YouGov, encompasses 60,000 instances, meticulously detailed and categorized by various factors such as election experiences, contextual data, demographic information (e.g., gender and race), political affiliations, and opinions on various policy issues. This dataset ensures a reliable representation of the population through its meticulous sampling methodology and validation processes, guaranteeing that it accurately reflects the diverse perspectives within the U.S. electorate. The dataset employs a matched random sampling methodology, with its representativeness further confirmed through a two-stage weighting process involving entropy balancing and iterative proportional fitting. Preprocessing steps, including sample matching, weighting, and vote validation, are conducted to ensure data quality and representativeness, thereby minimizing the risk of representative bias.

@@

We can use maths by including latex between dollar signs, for instance $\theta$.
## Model justification

@@

From the @tbl-model-summary-tableLogistic, with the constant variable, raceAsian, the intercept is -0.462 which means that the support for Biden decreases by about 0.784 units while all other variables remain the same. The following race, Hispanic (0.354), Middle Eastern (0.535), White (0.940), Native American (1.245), Two or more races (1.372) has stronger/ increasing their support for stronger/ increasing their support for Biden; in this case, the mixed race people have the strongest support for Biden. Yet, Black (−1.030) and Other  (−0.092) decrease support for Biden by looking at the coefficients.
# Discussion {#sec-Discussion}

>>>>

## Measurements 
The collected dataset from the Cooperative Election Study (CES) offers a comprehensive view of U.S. adult citizens' electoral behaviors, political opinions, and demographic characteristics. The CES 2022 dataset, gathered through an online survey by YouGov, encompasses 60,000 instances, meticulously detailed and categorized by various factors such as election experiences, contextual data, demographic information (e.g., gender and race), political affiliations, and opinions on various policy issues. This dataset ensures a reliable representation of the population through its meticulous sampling methodology and validation processes, guaranteeing that it accurately reflects the diverse perspectives within the U.S. electorate. The dataset employs a matched random sampling methodology, with its representativeness further confirmed through a two-stage weighting process involving entropy balancing and iterative proportional fitting. Preprocessing steps, including sample matching, weighting, and vote validation, are conducted to ensure data quality and representativeness, thereby minimizing the risk of representative bias.

@@

@@

From the @tbl-model-summary-tableLogistic , with the constant variable, raceAsian, the intercept is -0.462 which means that the support for Biden decreases by about 0.784 units while all other variables remain the same. The following race, Hispanic (0.354), Middle Eastern (0.535), White (0.940), Native American (1.245), Two or more races (1.372) has stronger/ increasing their support for stronger/ increasing their support for Biden; in this case, the mixed race people have the strongest support for Biden. Yet, Black (−1.030) and Other  (−0.092) decrease support for Biden by looking at the coefficients.
# Discussion {#sec-Discussion}
